Evaluation of Types

### 2020-05-16 evaluation/R/evaluate-type-analysis.Rmd

```{r, eval = TRUE, verbose = FALSE}
function_polymorphic_freq <-
union_data %>%
distinct(package_name, function_name, parameter_position, alternative_count) %>%
mutate(polymorphic = ifelse(alternative_count > 1, TRUE, is_polymorphic(alternative_count))) %>%
group_by(package_name, function_name) %>%
summarize(polymorphic_position_count = as.integer(sum(polymorphic))) %>%
ungroup() %>%
group_by(polymorphic_position_count) %>%
summarize(function_count = n()) %>%
ungroup() %>%
arrange(polymorphic_position_count)

@@

generate_macro("PercPolymorphicFunctions", 
               1.0 - function_polymorphic_freq %>% filter(polymorphic_position_count == "0") %>% pull(function_percentage),
               macro_filename)
```

>>>>

```{r, eval = TRUE, verbose = FALSE}
function_polymorphism <-
union_data %>%
distinct(package_name, function_name, parameter_position, alternative_count) %>%
mutate(polymorphic = ifelse(alternative_count > 1, TRUE, is_polymorphic(alternative_count))) %>%
group_by(package_name, function_name) %>%
summarize(polymorphic_position_count = as.integer(sum(polymorphic))) %>%
ungroup()

package_polymorphism <-
function_polymorphism %>%
group_by(package_name) %>%
summarize(monomorphic = all(polymorphic_position_count == 0)) %>%
ungroup()

function_polymorphic_freq <-
function_polymorphism %>%
group_by(polymorphic_position_count) %>%
summarize(function_count = n()) %>%
ungroup() %>%
arrange(polymorphic_position_count)

@@

generate_macro("PercPolymorphicFunctions", 
               1.0 - function_polymorphic_freq %>% filter(polymorphic_position_count == "0") %>% pull(function_percentage),
               macro_filename)

generate_macro("CountMonomorphicPackages", 
               package_polymorphism %>% pull(monomorphic) %>% sum(),
               macro_filename)
```
